Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-10-21 Code/R/RMarkdown/EntropyPlots.Rmd
paper update

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: pdf_document
#html_document
---

@@

#open3d()

#persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")

#-----
# mu <- seq(1, 10, length.out=200)
# alpha <- seq(-2, -20, length.out=200)
# 
# 
# entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
# entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
# entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
# entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
# entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
# 
# 
# fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
# 
# fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
# fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
# fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
# fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
# fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
# 
# 
# fig <- fig %>% layout(
#   scene = list(
#     xaxis = list(title = "alpha"),
#     yaxis = list(title = "mu"),
#     zaxis = list(title = "Entropy")
#   )
# )
# 
# fig

>>>>

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: html_document
#html_document
---

@@

open3d()

persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")

#-----
mu <- seq(1, 10, length.out=200)
alpha <- seq(-2, -20, length.out=200)

entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))

fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)

fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")

fig <- fig %>% layout(
  scene = list(
    xaxis = list(title = "alpha"),
    yaxis = list(title = "mu"),
    zaxis = list(title = "Entropy")
  )
)

fig

### 2023-10-21 Text/Articles/MIGARS_2024/The Entropy as a Proxy for Fully Developed Speckle.Rmd
paper update

# use some specific Tex packages if needed. 
# with_ifpdf: true
# with_cite: true
# amsmath need to be true to use with bookdown for referencing equations.
with_amsmath: true
# with_algorithmic: true
# with_array: true
# with_dblfloatfix: true

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{booktabs}
   - \usepackage{color}

bibliography: ["mybibfile.bib"]
output: rticles::ieee_article
#citation_sorting: none   ## used as sorting option of the biblatex package (if selected)
---

```{r Setup, echo=FALSE}
library(ggplot2)
library(ggthemes)

@@

@@

Entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
Shannon introduced it for a random variables in 1948~\cite{Shannon1948} as a measure of information and uncertainty. 
In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity~\cite{Wieczorkowski1999}.

@@

The article is structured as follows: 
Section~\ref{sec_02} describes

@@

## Statistical modeling of Intensity SAR data

The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions~\cite{Frery1997}. 
The first is suitable for fully developed speckle and can also be considered a limiting case within the $\mathcal{G}_I^0$ distribution.
Whereas the latter is appealing due to its versatility in accurately representing regions with various roughness characteristics~\cite{Cassetti2022}.
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
\begin{align}
	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\},\label{E:gamma1}\\
	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}},\label{E:gi01}
\end{align}
where, in~\eqref{E:gamma1} $\mu > 0$ is the mean; in~\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, and $\Gamma(\cdot)$ is the gamma function.

@@

Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$~\cite{Nascimento2010}.
In this way, we compute the expected value $\mu$ using the expression in~\eqref{E:rmom}, and we reparametrize~\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
\begin{align*}
	\mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*}
Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ is
\begin{multline}
		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)}\\ \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
\end{multline}

@@

Using~\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$ in~\eqref{E:gamma1} and $\mathcal{G}_I^0$ in~\eqref{E:gi02} based on~\cite{Cassetti2022, A.Ferreira2020}:
\begin{multline}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{multline}
\begin{multline}
\label{E:E-GIO}
H_{\mathcal{G}_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu \\
-\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)\\
-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L
\end{multline}
where $\psi^{(0)}(\cdot)$ and $\mathcal{B}(\cdot)$ are the digamma and beta functions, respectively.

The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including~\cite{vasicek1976test, Bert1992, Wieczorkowski1999, correa1995new}, who proposed estimators based on spacings.

Vasicek \cite{vasicek1976test}, used $f(z)=p$  to express $ H(Z)$ as
\begin{equation*}
	H(Z)= \int_0^1 \log\frac{\mathrm{d}}{\mathrm{d}p}Q(p)\mathrm{d}p,
\end{equation*}
where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics~\cite{AlOmari2019}.

@@

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es~\cite{Bert1992}, who proposed a new estimator of entropy given by:
\begin{multline}
\label{E:VanEs}
	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]\\
	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
\end{multline}

Van Es proved that, under general conditions,~\eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.

# Hypothesis tests

@@

This is an example of how to produce a plot in an RMarkdown reproducible paper.

First, you define the functions, or you load them from a library.

```{r Functions, echo=FALSE}
myfunction <- function(x){
  return(x^2)
}
```

Then, you produce and display the plot.
```{r MyFirstPlot, echo=FALSE, out.width="100%", fig.cap="My first function in a reproducible RMardown document"}
x <- seq(-3, 3, length.out=500)
y <- myfunction(x)

df <- data.frame(x, y)

ggplot(df, aes(x=x, y=y)) +
  geom_line() +
  xlab(expression(italic(x))) +
  ylab(expression(italic(y))) 
```

# Conclusions

<!-- An example of a floating figure using the graphicx package.
Note that \label must occur AFTER (or within) \caption.
For figures, \caption should occur after the \includegraphics.
Note that IEEEtran v1.7 and later has special internal code that
is designed to preserve the operation of \label within \caption
even when the captionsoff option is in effect. However, because
of issues like this, it may be the safest practice to put all your
\label just after \caption rather than within \caption{}.

Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
option should be used if it is desired that the figures are to be
displayed while in draft mode.

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{myfigure}
where an .eps filename suffix will be assumed under latex, 
and a .pdf suffix will be assumed for pdflatex; or what has been declared
via \DeclareGraphicsExtensions.
\caption{Simulation results for the network.}
\label{fig_sim}
\end{figure}

Note that the IEEE typically puts floats only at the top, even when this
results in a large percentage of a column being occupied by floats.

An example of a double column floating figure using two subfigures.
(The subfig.sty package must be loaded for this to work.)
The subfigure \label commands are set within each subfloat command,
and the \label for the overall figure must come after \caption.
\hfil is used as a separator to get equal spacing.
Watch out that the combined width of all the subfigures on a 
line do not exceed the text width or a line break will occur.

\begin{figure*}[!t]
\centering
\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
\label{fig_first_case}}
\hfil
\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
\label{fig_second_case}}
\caption{Simulation results for the network.}
\label{fig_sim}
\end{figure*}

Note that often IEEE papers with subfigures do not employ subfigure
captions (using the optional argument to \subfloat[]), but instead will
reference/describe all of them (a), (b), etc., within the main caption.
Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
labels, the optional argument to \subfloat must be present. If a
subcaption is not desired, just leave its contents blank,
e.g., \subfloat[].

An example of a floating table. Note that, for IEEE style tables, the
\caption command should come BEFORE the table and, given that table
captions serve much like titles, are usually capitalized except for words
such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
and up, which are usually not capitalized unless they are the first or
last word of the caption. Table text will default to \footnotesize as
the IEEE normally uses this smaller font for tables.
The \label must come after \caption as always.

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
if using array.sty, it might be a good idea to tweak the value of
\extrarowheight as needed to properly center the text within the cells
\caption{An Example of a Table}
\label{table_example}
\centering
% Some packages, such as MDW tools, offer better commands for making tables
% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{|c||c|}
\hline
One & Two\\
\hline
Three & Four\\
\hline
\end{tabular}
\end{table}

Note that the IEEE does not put floats in the very first column
- or typically anywhere on the first page for that matter. Also,
in-text middle ("here") positioning is typically not used, but it
is allowed and encouraged for Computer Society conferences (but
not Computer Society journals). Most IEEE journals/conferences use
top floats exclusively. 
Note that, LaTeX2e, unlike IEEE journals/conferences, places
footnotes above bottom floats. This can be corrected via the
\fnbelowfloat command of the stfloats package. -->

@@

Here are two sample references: @Feynman1963118 [@Dirac1953888].

>>>>

# use some specific Tex packages if needed. 
#with_ifpdf: true
#with_cite: true
# amsmath need to be true to use with bookdown for referencing equations.
with_amsmath: true
# with_algorithmic: true
# with_array: true
# with_dblfloatfix: true

# header-includes:
#    - \usepackage[english]{babel}
#    - \usepackage{bm,bbm}
#    - \usepackage{siunitx}
#    - \usepackage{graphicx}
#    - \usepackage{url}
#    - \usepackage[T1]{fontenc}
#    - \usepackage{booktabs}
#    - \usepackage{color}
#    - \usepackage{cite}

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{mathtools}

#bibliography: ../../Common/references.bib
bibliography:  ../../Common/references.bib
csl: ieee.csl
output: rticles::ieee_article
fig_caption: yes

#citation_sorting: none   ## used as sorting option of the biblatex package (if selected)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(plotly)
library(knitr)
library(rgl)
library(gtools)
library(stats4)
library(rmutil)
library(gsl)
library(invgamma)
```

@@

\newtheorem{lemma}{Lemma}

@@

Entropy is a fundamental concept in information theory with broad applications in fields like classification, pattern recognition, statistical physics, stochastic dynamics, and statistics.
Shannon introduced it for a random variables in 1948&nbsp;[@Shannon1948] as a measure of information and uncertainty. 
In statistics, Shannon entropy is a crucial descriptive parameter, particularly for assessing data dispersion and conducting tests for normality, exponentiality, and uniformity&nbsp;[@Wieczorkowski1999].

@@

The article is structured as follows: 
Section&nbsp;\ref{sec:2} describes

@@

## Statistical modeling of Intensity SAR data {#sec:2}

The primary models used for intensity SAR data include the Gamma and $\mathcal{G}_I^0$  distributions&nbsp;[@Frery1997]. 
The first is suitable for fully developed speckle and can also be considered a limiting case within the $\mathcal{G}_I^0$ distribution.
Whereas the latter is appealing due to its versatility in accurately representing regions with various roughness characteristics&nbsp;[@Cassetti2022].
We denote $Z \sim \Gamma_{\text{SAR}}(L, \mu)$ and $Z \sim G_I^0(\alpha, \gamma, L)$ to indicate that $Z$ follows the distributions characterized by the respective probability density functions:
\begin{align}
	f_Z(z;L, \mu)&=\frac{L^L}{\Gamma(L)\mu^L}z^{L-1}\exp\left\{-Lz/\mu\right\},\label{E:gamma1}\\
	f_Z(z; \alpha, \gamma, L)&=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}\cdot\frac{z^{L-1}}{(\gamma+Lz)^{L-\alpha}},\label{E:gi01}
\end{align}
where, in&nbsp;\eqref{E:gamma1} $\mu > 0$ is the mean; in&nbsp;\eqref{E:gi01}  $\gamma > 0$ is the scale, $\alpha < -1$ measures the roughness,  $L \geq 1$ is the number of looks, and $\Gamma(\cdot)$ is the gamma function.

@@

Even though the $\mathcal{G}_I^0$  distribution is defined by the parameters $\alpha$ and $\gamma$, SAR literature commonly utilizes the texture $\alpha$ and the mean $\mu$&nbsp;[@Nascimento2010].
In this way, we compute the expected value $\mu$ using the expression in&nbsp;\eqref{E:rmom}, and we reparametrize&nbsp;\eqref{E:gi01} using $\mu$, $\alpha$, and $L$. Then
\begin{align*}
	\mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\cdot\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{align*}
Thus, the probability density functions that characterize the $G_I^0(\mu, \alpha, L)$ is
\begin{multline}
		f_Z(z; \mu, \alpha, L)=\frac{L^L\Gamma(L-\alpha)}{\big(-\mu(\alpha+1)\big)^{\alpha}\Gamma(-\alpha)\Gamma(L)}\\ \frac{z^{L-1}}{\big(-\mu(\alpha+1)+Lz\big)^{L-\alpha}}.\label{E:gi02}
\end{multline}

@@

Using&nbsp;\eqref{E:entropy2}, we can express the Shannon entropy of $\Gamma_{\text{SAR}}$in&nbsp;\eqref{E:gamma1} and $\mathcal{G}_I^0$in&nbsp;\eqref{E:gi02} based on&nbsp;[@Cassetti2022, @Ferreira2020]:
\begin{multline}
\label{E:E-gamma}
H_{\Gamma_{\text{SAR}}}(L, \mu) =   L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) + \ln \mu, 
\end{multline}
\begin{multline}
\label{E:E-GIO}
H_{\mathcal{G}_I^0}(\mu, \alpha, L) =L -\ln L+\ln\Gamma(L)+(1-L)\psi^{(0)}(L) +\ln \mu \\
-\ln\Gamma(L-\alpha)+ (L-\alpha) \psi^{(0)}(L-\alpha)\\
-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L
\end{multline}
where $\psi^{(0)}(\cdot)$ and $\mathcal{B}(\cdot)$ are the digamma and beta functions, respectively.

The problem of non-parametric estimating of $H(Z)$ has been considered by many authors including&nbsp;[@vasicek1976test, @Bert1992, @Wieczorkowski1999, @correa1995new], who proposed estimators based on spacings.

Vasicek&nbsp;[@vasicek1976test], used $f(z)=p$  to express $ H(Z)$ as
\begin{equation*}
	H(Z)= \int_0^1 \log\frac{\mathrm{d}}{\mathrm{d}p}Q(p)\mathrm{d}p,
\end{equation*}
where $Q(p)=F^{-1}(p)=\inf\left\{z: F(z)\leq p\right\}$ is the quantile function. The derivative of $F^{-1}(p)$ is  estimated by a function of the order statistics&nbsp;[@AlOmari2019].

@@

Multiple authors have presented  adaptations to Vasicek's estimator, including Van Es&nbsp;[@Bert1992], who proposed a new estimator of entropy given by:
\begin{multline}
\label{E:VanEs}
	\widehat{H}_{\text{VE}}(\bm{Z})=\frac{1}{n-m}\sum_{i=1}^{n-m}\log\left[\frac{n+1}{m}\left(Z_{(i+m)}-Z_{(i)}\right)\right]\\
	+\sum_{k=m}^n\frac{1}{k}+\log\frac{m}{n+1}.
\end{multline}

Van Es proved that, under general conditions,\eqref{E:VanEs} converges almost surely to $H(Z)$ when $m, n\rightarrow\infty$,  $m/ \log(n)\rightarrow\infty$, and $m/n \rightarrow0$.
The author also proved the asymptotic normality of the estimator when $m, n\rightarrow\infty$ and $m=o(n^{1/2})$.

# Hypothesis testing based on non-parametric entropy
General asymptotic results for functions of spacings are detailed in&nbsp;\cite{Khashimov1990}, while Van Es&nbsp;\cite{Bert1992} has developed a correction for the case of Shannon entropy.
Following the work of these authors, the next result applies:

\begin{lemma}
Suppose that $f(\cdot)$ is a bounded density bounded away from zero and satisfies a Lipschitz condition on its support.
Then the next asymptotic results follow: If $m,n\rightarrow \infty$ and $m=o(n^{1/2})$, then:
\begin{equation}
\sqrt{n}\,\Big(\widehat{H}_{\text{VE}}+\int_{-\infty}^\infty f(z)\log f(z) \mathrm{d}z\Big)
\xrightarrow[]{\mathcal{D}}
\mathcal{N}(0,\operatorname{Var}(\log f(Z))),
\end{equation}
where $o(\cdot)$ represents the little-o and $\widehat{H}_{\text{VE}}$ is defined in expression \eqref{E:VanEs}.

\end{lemma}

Let us consider, starting from the previous lemma, the test of the null hypothesis $\mathcal{H}_0: T_{\mathcal{D}}=D_0$ as opposed to one of the other three:

\begin{equation}
\text{(i)}\, \mathcal{H}_1:T_{\mathcal{D}}\neq D_0, \, \, \text{(ii)}\, \mathcal{H}_1:T_{\mathcal{D}}> D_0, \, \, \text{or}\, \,  \text{(iii)}\, \mathcal{H}_1:T_{\mathcal{D}}< D_0. 
\end{equation}

For this purpose, we can use the test statistics:
\begin{equation}
Z_{m,n} = \frac{\sqrt{n}(\widehat{H}_{\text{VE}}-D_0)}{\sqrt{\operatorname{Var}(\log f(Z))}},
\end{equation}
So the null hypothesis should be rejected if (i) $Z_{n,m} > z_{\alpha/2}$ or $Z_{n,m} < - z_{\alpha/2}$ for $\Phi_{\mathcal N}(z_{\alpha/2})=1-\alpha/2$ and $\Phi_{\mathcal N}$ being the standard normal cdf, (ii) $Z_{n,m} > z_{\alpha/2}$ or (iii) $Z_{n,m} < - z_{\alpha/2}$.

The power function for case (i) (two-sided test) at $t\neq D_0$ is given by
\begin{multline*}
\pi_{m,n}(t)=1-\Phi_{m,n}\Big(z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big)\\+\Phi_{m,n}\Big(-z_{\alpha/2}-\frac{\sqrt{n}(Z_{m,n}-D_0)}{\sigma}\Big),
\end{multline*}
for a sequence of cdfs $\Phi_{m,n}(x)$ which tends uniformly to $\Phi_{\mathcal N}(z)$.

@@

We verify that the results of the non-parametric entropies for samples of different sizes converge towards the analytical entropies of $\Gamma_{\text{SAR}}(L, \mu)$ and $G^0(\alpha, \mu , L)$ as the sample size increases. 
%This indicates that the data appear to match the fully developed speckle hypothesis.

We assume distinct parameter values for $\mu \in \left\{1, 3, 10\right\}$,  $\alpha\in\left\{-1.5,-3,-5, -8\right\}$, and  $L \in\left\{1,2, 5, 8\right\}$.
We performed experiments to observe convergence under different scenarios, where each employed different sample sizes, i.e., $n\in \left\{9, 25, 49, 81, 121, 500, 5000\right\}$.

For each sample size, we performed $10.000$ samples. Fig. \ref{F4} shows convergence of mean non-parametric entropies, for $\mu=3$ and $L=2$.

In Fig. \ref{fig:PlotGammaSAR} We  see how the Shannon entropy of the Gamma-SAR model varies.

```{r FunctionsDefinitions, echo=FALSE}
entropy_gamma_sar <- function(L, mu) {

    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))

}

entropy_gI0 <- function(mu, alpha, L) {

  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))

  entropy <- term1 + term2 
  return(entropy)
}
```

```{r PlotGammaSAR, echo=FALSE, message=FALSE, warning=FALSE, out.width="80%", fig.show="hold", fig.align="center", fig.pos="hbt", fig.cap="Simulation results of Entropy for Gamma SAR"}
mu <- seq(.1, 10, length.out=500)

EntropyL1 <- entropy_gamma_sar(L=1, mu)
EntropyL3 <- entropy_gamma_sar(L=3, mu)
EntropyL8 <- entropy_gamma_sar(L=8, mu)
EntropyL12 <- entropy_gamma_sar(L=12, mu)
EntropyL100 <- entropy_gamma_sar(L=100, mu)

muEntropy <- data.frame(
  mu, EntropyL1, EntropyL3, EntropyL8, EntropyL12, EntropyL100
)

muEntropy.molten <- melt(muEntropy, measure.vars = 2:6, value.name = "Entropy", variable.name = "Looks")

ggplot(muEntropy.molten, aes(x=mu, y=Entropy, col=Looks)) +
  geom_line() +
  theme_pander()

```

@@
